---
title: "Case Study"
author: "Kimberly Lopez"
date: "2024-10-08"
output: html_document
---
```{r include=FALSE}
library(tidyverse)
library(leaflet)
library(p8105.datasets)
```

Setting Theme
```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Importing nyc_airbnb

```{r}
data(nyc_airbnb)
```

Brainstorming questions 


- What are max and min airbnb prices 
```{r}
nyc_airbnb|> 
  drop_na(price)|>
  select(price)|>
  pull(price)|>
  min()
```
The max is 10,000 and the min is 10.

- what are the average prices?
```{r}
nyc_airbnb|> 
  drop_na(price)|>
  pull(price)|>
  mean()
```
The average price is 145.3. 

- where are the prices going up and down over time?
```{r}
nyc_airbnb|>
  ggplot(aes(x=last_review,y=price))+
  geom_point()
```
```{r}
nyc_airbnb |>
  ggplot(aes(x = price, fill = neighbourhood_group)) +
  geom_histogram() +
  facet_grid(. ~ neighbourhood_group) +
  scale_x_continuous(limits = c(0, 250))
```

- whats the relationship between number of reviews and average review?
- does room type affect availability? (are private rooms less available)
```{r}
nyc_airbnb |>
  group_by(room_type) |>
  summarise(avg_price = mean(price, na.rm = TRUE)) |>
  ggplot(aes(x = room_type, y = avg_price, fill = room_type)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Price by Room Type in NYC Airbnb",
       x = "Room Type",
       y = "Average Price ($)") +
  theme_minimal()
```

- whats the location of the unit?
- what areas are popular 
```{r}
nyc_airbnb |>
  group_by(neighbourhood_group) |>
  summarise(total_reviews = sum(number_of_reviews, na.rm = TRUE)) |>
  arrange(desc(total_reviews))
```

- are there repeat hosts?
```{r}
nyc_airbnb %>%
  filter(calculated_host_listings_count > 1) %>%
  distinct(host_id, host_name, calculated_host_listings_count)|>
  arrange(desc(calculated_host_listings_count>34))
```
```{r}

```

- popularity = number of units? average price?
```{r}
nyc_airbnb|>
  ggplot(aes(x=review_scores_location, y=price))+
  geom_point()
```
```{r}
nyc_airbnb|>
  filter(neighbourhood_group== "Manhattan",
         price<1000)|>
  ggplot(aes(x=lat, y=long, color=price))+
  geom_point(alpha=.1)
```

Impact of neighborhood on price in numeric summary.
```{r}
nyc_airbnb|>
  filter(neighbourhood_group== "Manhattan",
         price<1000, 
         room_type=="Entire home/apt")|>
  group_by(neighbourhood)|>
  summarize(mean_price = mean(price))
```
```{r}
nyc_airbnb|>
  filter(neighbourhood_group== "Manhattan",
         price<1000, 
         room_type=="Entire home/apt")|>
  mutate(neighbourhood= fct_reorder(neighbourhood, price))|>
  ggplot(aes(x=neighbourhood, y=price))+
  geom_violin()+
  theme()
```

## Leaflet package 

- layer functiions on top of each other 
```{r}
nyc_airbnb|>
  filter(neighbourhood_group== "Manhattan",
         price<1000)|>
  slice(1:10)|>
  leaflet()|>
  addTiles()|>
  addMarkers(~lat, ~long)
           
```
* if you want this to be interactive, you have to change github_document to html_document and then save and knit 

Add *Circle Markers* instead of markers 
```{r}
nyc_airbnb|>
  filter(neighbourhood_group== "Manhattan",
         price<1000)|>
  slice(1:10)|>
  leaflet()|>
  addTiles()|>
  addCircleMarkers(~lat, ~long, radius=2)
```

```{r}
pal<- colorNumeric( 
  palette= "viridis",
  domain= nyc_airbnb$review_scores_location)
nyc_airbnb|>
  filter(neighbourhood_group== "Manhattan",
         price<1000)|>
  leaflet()|>
  addProviderTiles(providers$CartoDB.Positron)|>
  addCircleMarkers(~lat,
                   ~long,
                   color = ~pal(review_scores_location),
                   radius=2)
```

